Which fifteen-minutes neighborhoods are dead-ends? An analysis of the network attributes of fifteen-minute pedsheds

### 2024-10-21 paper/paper.Rmd
paper mehods edits

The origins we established are proxies for the centroids of neighborhoods in the urban and peri-urban areas of the city of Hamilton. Specifically, these are the centroids of Hamilton's Dissemination Areas (DA). A DA is composed of one or more neighboring dissemination blocks and represents the smallest standard geographic area for which all census data are disseminated in Canada. Data on urban and sub-urban boundaries and DAs were retrieved from @HamiltonData2023.

Destinations were established as the centroids of geohashed hexagons within the region of interest, where Hamilton's amenities are located, assuming that presence of amenities is a proxy to provision of opportunities. These destinations were chosen to avoid calculating travel times to each individual amenity. Instead, we used the geohashed polygons as destinations, identifying the amenities within each polygon and assuming that the centroid of each hexagon represents the location of the amenities within it. Specifically, we retrieved geohashing data for Hamilton using the H3 system (SOURCE) and generated child hexagons at resolution 13, with an average area of 43.87 $m^2$. Amenities location and typologies were downloaded from @OpenStreetMap2023.
<!--- 
To see the details of the destinations see notebook 02-OSM-Amenities.Rmd in folder data-raw
--->

@@

In this study, we calculate cumulative accessibility scores by summing the number of amenities within urban and suburban walksheds, categorized into the four types provided by the data source: financial, sustenance, healthcare, and library.
<!--- 
To see the details of the accessibility calculations see notebook 04-Accessibility-Calculations.Rmd in folder data-raw
--->

>>>>

The origins we established are proxies for the centroids of neighborhoods in the urban and peri-urban areas of the city of Hamilton. Specifically, these are the centroids of Hamilton's Dissemination Areas (DA). A DA is composed of one or more neighboring dissemination blocks and represents the smallest standard geographic area for which all census data are disseminated in Canada. Data on urban and sub-urban boundaries, DAs,and population data in 2016 were retrieved from @HamiltonData2023.

Destinations were established as the centroids of geohashed hexagons within the region of interest, where Hamilton's amenities are located, assuming that presence of amenities is a proxy to provision of opportunities. These destinations were chosen to avoid calculating travel times to each individual amenity. Instead, we used the geohashed polygons as destinations, identifying the amenities within each polygon and assuming that the centroid of each hexagon represents the location of the amenities within it. Specifically, we retrieved geohashing data for Hamilton using the H3 system @h3Package and generated child hexagons at resolution 13, with an average area of 43.87 $m^2$. Amenities location and their typology were downloaded from @OpenStreetMap2023. 
<!--- 
To see the details of the destinations see notebook 02-OSM-Amenities.Rmd in folder data-raw
--->

@@

In this study, we calculate cumulative accessibility scores by summing the number of amenities within urban and suburban walksheds, categorized into the four types provided by the data source: financial, sustenance, healthcare, and library. Additionally, we extract population data of each walkshed. Summary statistics of population are also included in the analysis.

Additionally, the accessibility assessment of is completed by obtaining summary statistics of travel times in urban and suburban walksheds. To study the impact of urban and suburban walksheds on walking decisions, minimum and mean travel times to destinations are introduced into time-decay functions for walking decisions, as developed by Milward (2013). These are active travel impedance functions based on data from Canada.

<!--- 
To see the details of the accessibility calculations, summary statistics, and obtention of impedance functions see notebook 04-Accessibility-Calculations.Rmd in folder data-raw
--->
